Innovations Report: Procedural Fur System

### 2018-03-07 docs/paper.tex
more on docs

>>>>

His final comments were in regards to the user interface, suggesting that I make controls similar to their counterparts in existing software wherever possible. Changing the camera controls to match those in Maya was suggested as it would provide a familiar user experience when manipulating the viewport. The ability to create new nodes by pressing the tab key as opposed to right click was also suggested, as this is the standard in node editors, such as those in Maya and Nuke.
